\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-05 R/classify_species.Rmd
experimentin with variable importance figures
combining MDA and MDG into a single figure?

ggsave(filename = here::here("analysis","figures", "confMat_species_valid.pdf"), width = 15, height = 15)
```

@@

```{r varImp_byWavelength_plot, fig.height=6, fig.width=10}
ggplot(imp, aes(x=wavelength_nm,  
                y=MeanDecreaseAccuracy)) + 
  # add bars where each height is equal to the variable importance metric
  geom_col(aes(fill = MeanDecreaseAccuracy), color = NA) +
  theme_minimal() + 
  labs(x = "Wavelength (nm)", 
       y = "Variable importance (MDA)",
       title = "Variable Importance: Mean Decrease Accuracy (MDA) vs. Wavelength",
       fill = "MDA")  + 
  scale_fill_gradient(low = "#d9d9d9", high = "#43a2ca")
```

```{r varImp_Gini, fig.height=6, fig.width=10}
ggplot(imp, aes(x = wavelength_nm,  
                y = MeanDecreaseGini)) + 
  # add bars where each height is equal to the variable importance metric
  geom_col(aes(fill = MeanDecreaseGini), color = NA) +
  theme_minimal() + 
  labs(x = "Wavelength (nm)", 
       y = "Variable importance (MDG)",
       title = "Variable Importance: Mean Decrease Gini (MDG) vs. Wavelength",
       fill = "MDG")  + 
  scale_fill_gradient(low = "#d9d9d9", high = "#43a2ca")
```

>>>>

# save confusion matrix to file 
ggsave(filename = here::here("analysis","figures", "confMat_species_valid.pdf"), width = 15, height = 15)
```

@@

```{r varImp_byWavelength_plot, fig.height=6, fig.width=10}
varImp_MDA_species <- ggplot(imp, aes(x=wavelength_nm,  
                y=MeanDecreaseAccuracy)) + 
  # add bars where each height is equal to the variable importance metric
  geom_col(aes(fill = MeanDecreaseAccuracy), color = NA) +
  theme_minimal() + 
  labs(x = "Wavelength (nm)\n", 
       y = "Variable importance \nMean Decrease in Accuracy (MDA)\n",
       #title = "Variable Importance: Mean Decrease Accuracy (MDA)",
       fill = "MDA")  + 
  scale_fill_gradient(low = "#d9d9d9", high = "#43a2ca") + 
   theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16))

varImp_MDA_species
```

```{r varImp_Gini, fig.height=6, fig.width=10}
varImp_Gini_species <- ggplot(imp, aes(x = wavelength_nm,  
                y = MeanDecreaseGini)) + 
  # add bars where each height is equal to the variable importance metric
  geom_col(aes(fill = MeanDecreaseGini), color = NA) +
  theme_minimal() + 
  labs(x = "Wavelength (nm)", 
       y = "Variable importance \nMean Decrease Gini (MDG)\n",
       #title = "Variable Importance: Mean Decrease Gini (MDG)",
       fill = "MDG")  + 
  scale_fill_gradient(low = "#d9d9d9", high = "#43a2ca") + 
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        legend.text = element_text(size = 14))

varImp_Gini_species
```

Single figure with both variable importance plots:

```{r varmImp_species}
library(ggpubr)

ggpubr::ggarrange(varImp_MDA_species, varImp_Gini_species, nrow = 2)

# save confusion matrix to file 
ggsave(filename = here::here("analysis","figures", "varImp_species.pdf"), width = 10, height = 10)
```

### 2020-11-05 R/clean_spectral_data.Rmd
experimentin with variable importance figures
combining MDA and MDG into a single figure?

```{r, eval = FALSE, include = "FALSE", warning=FALSE, fig.height=8, fig.width=10}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID)) +
  geom_path(alpha = .2, color = "#1c9099") +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n') + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=5) +
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14))

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 8)
```

>>>>

```{r, warning=FALSE, fig.height=8, fig.width=10}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID)) +
  geom_path(alpha = .2, color = "#1c9099") +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n') + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=5) +
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14))

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 11)
```

### 2020-11-05 analysis/paper/paper.Rmd
experimentin with variable importance figures
combining MDA and MDG into a single figure?

knitr::kable(x = df, 
             # set column names
             col.names = c("Overall Accuracy [%]",
                           "Species Classification",
                           "Genus Classification"),
             # center align text in the columns
             align = c("c", "c", "c"),
             format = "simple")
```

@@

Confusion matrix for species predictions (Figure \@ref(fig:fig-confMatSpecies))
Confusion matrix for genus predictions (Figure \@ref(fig:fig-confMatGenus))

Figure - variable importance vs wavelength
Figure - multi-year observations of individual plants?

@@

```{r fig-confMatGenus, fig.cap ="Confusion matrix Species", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "confMat_genus_valid.pdf"))
```

@@

>>>>

knitr::kable(x = df, 
             # set column names
             col.names = c("Overall Classification Accuracy [%]",
                           "Species",
                           "Genus"),
             # center align text in the columns
             align = c("c", "c", "c"),
             format = "simple")
```

@@

Confusion matrix for species classification (Figure \@ref(fig:fig-confMatSpecies))

Confusion matrix for genus classification (Figure \@ref(fig:fig-confMatGenus))

Variable importance for species classification (Figure \@ref(fig:varImpSpecies))

Figure - multi-year observations of individual plants?

@@

```{r fig-confMatGenus, fig.cap ="Confusion matrix Genus", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "confMat_genus_valid.pdf"))
```

@@

## Figure 6 {-}

```{r fig-varImpSpecies, fig.cap ="Variable Importance Species", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "varImp_species.pdf"))
```
